\section{\fontsize{12}{15}\selectfont Background Knowledge}

\subsection{Eye movements}\label{eye}
To understand how speed reading is possible, it's important to know some of the basics behind how the eyes move.

When you read, visually analyse or look for something, your eyes are doing a series of movements called \textit{saccades}. Between these movements your eyes shortly fixate on elements. These stops are called \textit{fixations}. Each fixations lasts around 200-300 ms, so the eyes are quickly looking around a scene to find new details to fixate on. The movements of the eyes themselves reach speeds of up to 500 degrees a second \cite{eyeMovement}.

There is generally three types of saccades: pursuit, vergence and vestibular. \textit{Pursuit} is when the eyes are trying to fixate on a moving object. Generally, in these cases, the saccades are slower, as the eyes are following the target and not going back and forth between different targets \cite{eyeMovement}.
\textit{Vergence} is the inwards movement of the eyes, trying to focus on an approaching object \cite{eyeMovement}.

\textit{Vestibular} movements happen when the eyes rotate to compensate for body or head movements. This is caused by visual stimulation, but mostly by the vestibular organ in the ears. This is also also why your sight gets blurry when you're dizzy.

In the case of reading, it's also important to talk about the different kinds of small saccades the eyes are capable of. \textit{Nystagmus} are tiny and quick movements in the eyes, which causes a tremor in the vision \cite{eyeMovement}. You will notice it when staring intently at a fixed point. It's believed that this is a precaution in the eyes to make the nerve cells keep firing by continuously stimulating them. Furthermore, the eyes also experience small \textit{drifts}. These are believed to be the results of a less-than-perfect control of the oculomotor, resulting in the eyes slowly drifting to one side. To accommodate this, the eyes make tiny saccades, called \textit{microsaccades}, to realign themselves \cite{eyeMovement}.

Another important aspect to the understanding of reading is \textit{saccade latency}. Every time a saccade is made, calculations are needed to approximate the destination of the fixation on a desired target. Even if excluding the uncertainty of where to move the eyes, it would still take 150-175 ms for the initial "request" of moving the eyes to the actual start of the movement. Cognitive processes further increases this latency, but also increases accuracy, meaning your fixation falls closer to the point of interest.

%\textbf{(Gustav: maybe write something about cognitive processes from Perception book here)}

During the saccade, everything is a blur. Certain parts associated with processing visual inputs are halted during saccades. This process is called \textit{saccadic suppression}, but is independent of the lexical processing\footnote{Cognitive processing of language (words, vocabulary).}, which means a reader is able to process a read text in parallel with saccades \cite{eyeMovement}.

A fixation on a given word is not needed in order to read it. Your attention can be shifted to targets in or outside the foveal vision \cite{eyeMovement}. It is even possible to focus your attention on multiple targets simultaneously \cite{simAttention}, but it is not possible to make a saccade without shifting attention to the fixation \cite{eyeMovement}.