\documentclass[jou,apacite]{apa6}
%\usepackage[style=apa,backend=biber]{biblatex}

\title{Analysis of Speed Reading in Contemporary Literature}
\shorttitle{Does Rapid Serial Visual Presentation (RSVP) make us faster readers?}

\fourauthors{Mathias K. Berthelsen}{Gustav Dahl}{Benjamin N. Overgaard}{Andreas M. Thomsen}
\fouraffiliations{Study no. 20115689}{Study no. 20113263}{Study no. 20113220}{Study no. 20113259}

\abstract{This paper will investigate the speed reading technique known as Rapid Serial Visual Presentation (RSVP), as well as how it relates to other topics, such as eye movement and modes for reading. The goal of this paper is to analyze contemporary theory and literature and discuss the different points of view in regards to speed reading.

Rapid Serial Visual Presentation is a speed reading technique that shows words from a text one at a time. The main reason this is a speed reading technique is that it eliminates the need of saccades. The optimal recognition position of a word and the processing speed of different words also comes into account to increase the reading speed. However, the goal of reading a text can differ which can impact the effectiveness of RSVP. As an example, if a reader is reading a text to memorize it, they go a couple of words back in the text in the text to properly remember them, this is something that RSVP doesn't allow.}

\rightheader{RAPID SERIAL VISUAL PRESENTATION}
\leftheader{MTA14737}

\begin{document}
\maketitle

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Perception, reading}

%\keywords{Speed reading, reading, RSVP, comprehension, eye saccades} % NOT required for Proceedings

\input{introduction}
\input{eyeMovements}
\input{attention}
\input{orp}
\input{readingProcess}
\input{subvocal}
\input{speedreading}
\input{critiq_speedReading}
\input{discussionandconclusion}

%\include{helpGuide} %% GUSTAV'S GUIDE: look at this for how to insert figures, quotes, etc.
\bibliography{references}
%\bibliography{sample}
\end{document}
