\subsection{Findings}
GUSTAV. They like Maya
\subsubsection{Keyframing Concept}
Through our observations of the artists' use of Maya and from feature request by the artists, we found that the most important feature was keyframes. A keyframe is an event and/or change in one or more parameters over time. Each keyframe corresponds to a point in time, meaning that when the animation reaches this point in time, the values of this keyframe are dominant. Usually this means that in between keyframes some interpolation is happening. This interpolation is per default either linear or uses Bézier curves, but can be manipulated in a graph editor. Anything that can be represented by numbers can be manipulated through keyframes.

But games are dynamic, not linear, so this means keyframes can't be associated with a point in time. Specifically for this game, the camera settings would change according to the player's movement, so keyframes needed to be associated with this. Furthermore, the player had to walk on a fixed path, which made the interpolation significantly simpler.

A quick paper prototype of the initial concept showed promise, and the idea of associating keyframes with player position was easily understood. To avoid confusion, these keyframes were renamed \textit{framings}. A framing consists of an \textit{influence point} and a camera (Andreas' tegning). When the player's position is the same as an influence point, that framing will dominate, meaning the main camera will use the camera settings of the associated camera. Moving between influence points causes an interpolation between each camera setting. This interpolation can be manipulated in a graph editor, as in Maya.

Figure text: The red nodes are indicating the player path, and the yellow nodes are the influence points.