\section{Introduction}
%BASED ON PRELIMIANARY RESEARCH, TOOLS SHOULD BE DEVELOPED WITH A MODULAR MINDSET AND ALLOW FOR TWEAKABLE PARAMTERS and stuff

%Describe basic concept of the product (context)
%We have a collaboration with TAW
%They make 3D point n click game
%Framing system
%Path system

This project is based on a collaboration between Medialogy and a group of artists from The Animation Workshop (TAW) in Viborg. As their bachelor project, the students at TAW developed a 3D point 'n click game, \textit{FEELS}, for the iPad using the Unity game engine. The TAW project spanned two semesters (pre-production and production), whereas this Medialogy project lasted only the first semester. Three additional programmers have also been working full-time on the project.

During the collaboration, it was decided that we should focus on developing a camera system for the game. This tool should empower the artists to make a game with the required aesthetics, so that the artists didn't have to worry about technical details. It should be simple to set up and function in a similar fashion as other 3D applications that the TAW students have been trained in during their three-year education. The camera tool was chosen, since it does not directly influence and interfere with the gameplay, making it easier for the other programmers to work directly on the game.

Before we began designing and implementing the tool, we conducted several preliminary studies to get an understanding of how game development tools should be made. We visited two game companies (KnapNok Games and Unity Studios), as well as conducting an online survey to gather, information about game development tools. The key findings were that the tool should be developed in a modular fashion and allow the user to tweak as many parameters as deemed necessary. Additional notes from the studies can be found in \textbf{APPENDIX X}.